---
title: "Intro to LinReg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to LinReg}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(ggplot2)
library(gridExtra)
library(LinReg)
```

When working with linear regression models you must:

* Let the computer do the calculations (much faster!)

* Describe the formula for the model and specify data

* Execute the program

The LinReg package makes these steps fast and easy. This document introduces you to LinReg's basic set of tools, and shows you how to apply them to your dataset.

## Examples, how-to:

### Model specification
Type in formula and data as input to `linreg`-function.

```{r, echo = TRUE, message = FALSE}
mod <- linreg(formula = Sepal.Width ~ Sepal.Length, data = iris)
```

### Model parameters
For beta coefficients, use `print()` as follows:

```{r, echo = TRUE, message = FALSE, warning=FALSE}
print(mod)
```

### Model plot
`LinReg` also comes with a smoking hot theme, just add `theme_liu()` and see for yourself! For residuals plot (with awesome theme), use `plot()` as follows:

```{r, echo = TRUE, message = FALSE}
plot(mod)
```

